My title\thanks{Code and data are available at: LINK.}

### 2024-02-08 paper/paper.qmd
making penguins

```{r}
ggplot(data = penguins,
       aes(x = flipper_length_mm,
           y = body_mass_g)) +
  geom_point(aes(color = species, shape = sex),
             size = 10,
             alpha = 1) +
  scale_color_manual(values = c("red", "pink", "red")) +
  labs(
    title = "Penguins are mean, ur mom's house",
    subtitle = "Toe length and mass for ADeLIe, ChINSTRAP and gEnToo peNGuiNS",
    x = "Flipper length (houses)",
    y = "Body mass (bluberries)",
    color = "Penguin species"
  ) +
  theme_minimal() +
  theme(
    legend.position = c(0.7, 0.9),
    plot.title.position = "plot",
    plot.caption = element_text(hjust = 0, face = "italic"),
    plot.caption.position = "plot"
  )

>>>>

We are interested in penguins and their silly business (@fig-penguins)

```{r}
#| label: fig-penguins

ggplot(data = penguins,
       aes(x = flipper_length_mm,
           y = body_mass_g)) +
  geom_point(aes(color = species, shape = sex),
             size = 10,
             alpha = 1) +
  scale_color_manual(values = c("red", "pink", "red")) +
  labs(
    title = "Penguins are mean, ur mom's house",
    subtitle = "Toe length and mass for ADeLIe, ChINSTRAP and gEnToo peNGuiNS",
    x = "Flipper length (houses)",
    y = "Body mass (bluberries)",
    color = "Penguin species"
  ) +
  theme_minimal() +
  theme(
    legend.position = c(0.7, 0.9),
    plot.title.position = "plot",
    plot.caption = element_text(hjust = 0, face = "italic"),
    plot.caption.position = "plot"
  )

### 2024-02-08 paper/paper.tex
making penguins

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, interior hidden, sharp corners, enhanced, breakable, frame hidden, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

@@

{\centering \includegraphics{paper_files/figure-pdf/unnamed-chunk-8-1.pdf}

@@

>>>>

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, sharp corners, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

We are interested in penguins and their silly business
(Figure~\ref{fig-penguins})

@@

{\centering \includegraphics{paper_files/figure-pdf/fig-penguins-1.pdf}

@@

\caption{\label{fig-penguins}\textbf{?(caption)}}
